### 2010-03-11 doc/tech_doc/a-rex/arex_tech_doc.tex
add cache lifetime feature, part of fix for 1851

\begin{itemize}
\item \emph{cache-clean} - This tool is used periodically by the A-REX to
  keep the size of each cache within the configured
  limits.\\
  \emph{cache-clean -h} gives a list of options. The most
  useful option for administrators is \emph{-s}, which does not delete
  anything, but gives summary information on the files in the cache,
  including information on the ages of the files in the cache.\\
  It is not recommended to run \emph{cache-clean} manually to clean up
  the cache, unless it is desired to temporarily clean up the cache with
  different size limits to those specified in the configuration, or to
  improve performance by running it on the file system's local node as
  mentioned above.
\item \emph{cache-list} - This tool is used to list all files present
  in each cache. It simply reads through all the \emph{.meta }files
  and prints to stdout a list of all URLs stored in each cache and
  their corresponding cache filename, one per line.
\end{itemize}

@@

>>>>

\begin{itemize}
\item \emph{cache-clean} - This tool is used periodically by the A-REX to
  keep the size of each cache within the configured
  limits.\\
  \emph{cache-clean -h} gives a list of options. The most
  useful option for administrators is \emph{-s}, which does not delete
  anything, but gives summary information on the files in the cache,
  including information on the ages of the files in the cache.\\
  It is not recommended to run \emph{cache-clean} manually to clean up
  the cache, unless it is desired to temporarily clean up the cache with
  different size limits to those specified in the configuration, or to
  improve performance by running it on the file system's local node as
  mentioned above.
\item \emph{cache-list} - This tool is used to list all files present
  in each cache or, given a list of URLs as arguments, shows the
  location of each URL in the cache if present. In the first case it
  simply reads through all the \emph{.meta }files and prints to stdout
  a list of all URLs stored in each cache and their corresponding
  cache filename, one per line. In the second case the cache filename
  of each URL is calculated and then each cache is checked for the
  existence of the file.
\end{itemize}

@@

\item \textbf{\textit{cachelifetime}}\textit{=lifetime} - if cache
  cleaning is enabled, files accessed less recently than the
  \emph{lifetime} time period will be deleted. Example values of this
  option are 1800, 90s, 24h, 30d. When no suffix is given the unit is
  seconds.
